Design, Implementation, and Evaluation of Open Power Quality

### 2020-07-16 cover-letter/reviewer-3.tex
save reviewer letters.

{\bf Comments from Reviewer 2:}

{\em (1) In my opinion the paper is too long. Getting through the whole paper is very tiring. It seems that the maximum length of a scientific article (not including appendix) should be 20–22 pages. Maybe some of the descriptions can be moved to the appendix.}

{\em (2) I suggest a typical layout used in the articles: Introduction, Methods, Results and Discussion, Conclusions. This template is also recommended by Journal (see Instructions for Authors).}

{\em (3) Because this is a scientific article, the aims of the work and the research gap should be more clearly highlighted. I also suggest to improve the conclusions, delete the description of the work carried out (it is already well known) and focus on the most important conclusions and the future research. }

{\em (4) The quality of Figures should be corrected, their descriptions, especially axis descriptions are unreadable.}

>>>>

{\bf Comments from Reviewer 3:}

{\em (1) Ideas presented in the article are well described, including their advantages and limitations. The introduction covers the basic overview of the topic. It is hard to point out a single specific problem of the article since authors are very precisely defining the structure and following this in the article body (some abbreviations are used before explanation (e.g. THD). Figures 6c and 6d are missing).}

Thanks for the kind words.

{\em (2) Generally, I am looking for a scientific background of the article – and it is tough to find. Authors have already realized a lot of engineering work (and their presentation is precise); nevertheless, a deep (or deeper) scientific level is missing from my point of view. Anyway, the paper might be useful for future readers and can inspire them in their work. Therefore I recommend it for publishing.}
